Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-09-05 GWLDCII.tex
added/edited pictures as discussed

@@

\newcommand{\drawnumbers}{
  \foreach \i in {1,2,...,\n} {
  \pgfmathsetmacro{\x}{\angle*\i}
  \draw (\x:\radius*1.15) node {\footnotesize \i};
}
}

@@

@@

\begin{lem}\label{lem sian} \sanote{should this be rephrased more similarly to the philosophy of Lemma 4.4, allowing non-supporting vertices to be added in or taken out?}
  Let $W$ be a weakly admissible WLD with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs.
  \begin{enumerate}
    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 on one side of it and nothing else on that side.\label{item big and 2}
    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
  \end{enumerate}
\end{lem}
\note{Should this lemma have pictures}

@@

\note{I would like to discuss the angles of the arrows in fig 14}

@@

@@

	\draw[->,shorten >=2pt,red,thick] (1.5*\angle + -1*\move:\radius) to[bend left = 45] (\angle*1:\radius); %p
	\draw[->,shorten >=2pt,red,thick] (1.5*\angle:\radius) to[bend right = 45] (\angle*2:\radius); %q
	\draw[->,shorten >=2pt,red,thick] (4.5*\angle:\radius) to[bend left = 45] (\angle*4:\radius); %r

@@

	\draw[->,shorten >=2pt,red,thick] (1.5*\angle + -1*\move:\radius) to[bend right = 45] (\angle*2:\radius); %p
	\draw[->,shorten >=2pt,red,thick] (5.5*\angle:\radius) to[bend left = 45] (\angle*5:\radius); %q
	\draw[->,shorten >=2pt,red,thick] (4.5*\angle:\radius) to[bend left = 45] (\angle*4:\radius); %r

@@

	\draw[->,shorten >=2pt,red,thick] (6.5*\angle:\radius) to[bend left = 45] (\angle*6:\radius); %p
	\draw[->,shorten >=2pt,red,thick] (5.5*\angle:\radius) to[bend left = 45] (\angle*5:\radius); %q
	\draw[->,shorten >=2pt,red,thick] (4.5*\angle:\radius) to[bend left = 45] (\angle*4:\radius); %r

@@

	\draw[->,shorten >=2pt,red,thick] (6.5*\angle:\radius) to[bend right = 45] (\angle*7:\radius); %p
	\draw[->,shorten >=2pt,red,thick] (5.5*\angle:\radius) to[bend right = 45] (\angle*6:\radius); %q
	\draw[->,shorten >=2pt,red,thick] (4.5*\angle:\radius) to[bend right = 45] (\angle*5:\radius); %r

@@

	\draw[->,shorten >=2pt,red,thick] (6.5*\angle:\radius) to[bend right = 45] (\angle*7:\radius); %p
	\draw[->,shorten >=2pt,red,thick] (5.5*\angle:\radius) to[bend right = 45] (\angle*6:\radius); %q
	\draw[->,shorten >=2pt,red,thick] (1.5*\angle + 1*\move:\radius) to[bend left = 45] (\angle*1:\radius); %r

@@

	\draw[->,shorten >=2pt,red,thick] (6.5*\angle:\radius) to[bend right = 45] (\angle*7:\radius); %p
	\draw[->,shorten >=2pt,red,thick] (1.5*\angle:\radius) to[bend left = 45] (\angle*1:\radius); %q
	\draw[->,shorten >=2pt,red,thick] (1.5*\angle + \move:\radius) to[bend right = 45] (\angle*2:\radius); %r

@@

\begin{figure}
\[
\begin{tikzpicture}[baseline=(current bounding box.east),rotate=-20]
\begin{scope}
	\drawWLDfragment[8]{3}{0.4} 
	%\drawnumberspartial % use this to debug
	\newnode[left]{1}{i-1}
	\newnode[below]{2}{i}
	\newnode[below]{7}{m}
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
		\newpropbend{1.7}{7.2}{60}
		\draw[smallpropagator,blue] (\zero+7.8*\step:\radius*1.1) to[bend left = 55] (\zero + 10*\step:\radius*1.1);
		\node at (\zero + 1.2*\step:\radius*0.5) {\footnotesize $p$};
	\end{scope}
	\node[align = center,black] at (\zero + \step*4.5:\radius*0.65) {\em \footnotesize propagators \\ \footnotesize \em inside $p$};
	\draw[->,shorten >=2pt,thick,gray] (\zero + 1.6*\step:\radius) to[bend left = 45] (\zero + 1*\step:\radius); %p
	\draw[->,shorten >=2pt,thick,gray] (\zero + 7.9*\step:\radius) to[bend left = 45] (\zero + 7*\step:\radius); 
	\node[align = center,black] at (\zero + 6.8*\step:1.5*\radius) {\em \footnotesize If $m \in I_i$ then \\ \em \footnotesize it was contributed by \\ \em \footnotesize the blue propagator};
\end{scope}
\end{tikzpicture}
\qquad 
\begin{tikzpicture}[baseline=(current bounding box.east),rotate=-20]
	\begin{scope}
	\drawWLDfragment[8]{3}{0.4}  
	%\drawnumberspartial % use this to debug
	\newnode[left]{1}{i}
	\newnode[below]{2}{i+1}
	\newnode[below]{7}{j}
	\centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 1.5*\step:\zero+1.56*\step:\radius);
	\draw[->,shorten >=2pt,thick,gray] (\zero + 1.45*\step:\radius) to[bend left = 45] (\zero + 1*\step:\radius); %p
	\draw[->,shorten >=2pt,thick,gray] (\zero + 1.61*\step:\radius) to[bend right = 45] (\zero + 2*\step:\radius); %q 
	\draw[->,shorten >=2pt,thick,gray] (\zero + 7.7*\step:\radius) to[bend left = 45] (\zero + 7*\step:\radius); %blue
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
		\newpropbend{1.6}{7.2}{40} % q
		\draw[smallpropagator] (\zero+1.5*\step:\radius*1.1) to[bend right = 40] (\zero  - 3*\step:\radius*1.1); % p
		\draw[smallpropagator,blue] (\zero+7.6*\step:\radius*1.1) to[bend left = 55] (\zero + 10*\step:\radius*1.1);
		\node at (\zero + 5*\step:\radius*0.3) {\footnotesize $q$};
		\node at (\zero + 1*\step:\radius*0.6) {\footnotesize $p$};
	\end{scope}
	\node[align = center,black] at (\zero + \step*4.5:\radius*0.75) {\em \footnotesize propagators \\ \footnotesize \em inside $q$};
	\node[align = center] at (\zero + 1.5*\step:\radius*1.5) {\footnotesize \em No \\ \footnotesize \em propagators \\ \footnotesize \em between \\ \footnotesize \em $p$ and $q$ \\ \footnotesize \em here};
	\node[align = center,black] at (\zero + 6.8*\step:1.5*\radius) {\em \footnotesize If $j \in I_i$ then \\ \em \footnotesize it was contributed by \\ \em \footnotesize the blue propagator};
\end{scope}
\end{tikzpicture}
\]
  \caption{The two cases in the proof that no factors of $\Delta_{I_i}$ have degree 3 or more.{\color{violet}First picture: I thought $I_i(p) = i$. Doesn't the arrow say that $I_i(p) = i-1$?}}\label{fig no big factors}
\end{figure}

>>>>

 % used for showing which propagator assigns to which vertex in the last section
\pgfmathsetmacro{\arrowangle}{75}
\tikzstyle{propassignment} = [->,shorten >=2pt,thick]

@@

\newcommand{\drawnumbers}{
  \foreach \i in {1,2,...,\n} {
  \pgfmathsetmacro{\x}{\angle*\i}
  \draw (\x:\radius*1.25) node {\footnotesize \i};
}
}

@@

\begin{figure}[h]
\[
\begin{tikzpicture}[baseline=(current bounding box.north)]
  \begin{scope}
  \drawWLDfragment[7]{3}{0.4} 
  %\drawnumberspartial % use this to debug
  \centerarc[linehighlight](0,0)(\zero + 1.43*\step:\zero+6.6*\step:\radius)
  \newnode{1}{}
  \newnode{3.55}{}
  \newnode{4.45}{}
  \newnode{7}{}
    \begin{scope}
    \clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
  \newpropbend{1.3}{6.7}{20}
  \newpropbend{2.9}{5.1}{45}
  \end{scope}
  \node[align=center] at (\zero + 4*\step:\radius*1.43) {\footnotesize \em $\leq 6$ vertices in the \\ \footnotesize \em highlighted region};
\end{scope}
\end{tikzpicture}
\qquad \qquad \qquad
\begin{tikzpicture}[baseline=(current bounding box.north)]
  \begin{scope}
  \drawWLDfragment[7]{3}{0.4} 
  %\drawnumberspartial % use this to debug
  \centerarc[linehighlight](0,0)(\zero + 3.67*\step:\zero+4.43*\step:\radius)
  \newnode{1}{i}
  \newnode[below]{2}{i+1\ \ \ }
  \newnode[below]{3}{i+2}
  \newnode[below]{5}{j+1}
  \newnode[below]{6}{\quad j+2}
  \newnode[right]{7}{j+3}
      \begin{scope}
    \clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
  \newpropbend{1.35}{3.6}{55}
  \newpropbend{4.4}{6.6}{55}
  \end{scope}
  \node[align=center] at (\zero + 4*\step:\radius*1.5) {\footnotesize \em $\leq 2$ vertices in the highlighted \\ \footnotesize \em region, and  no other propagators \\ \em \footnotesize end in the highlighted region};
\end{scope}
\end{tikzpicture}
\]
\caption{The two configurations described in Lemma~\ref{lem sian}; every weakly admissible Wilson loop diagram with no non-supporting vertices supports at least one example of at least one of these configurations.}\label{fig: small configs}
\end{figure}

@@

\begin{lem}\label{lem sian} \sanote{should this be rephrased more similarly to the philosophy of Lemma 4.4, allowing non-supporting vertices to be added in or taken out?}
  Let $W$ be a weakly admissible WLD with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs:
  \begin{enumerate}
    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 on one side of it and nothing else on that side.\label{item big and 2}
    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
  \end{enumerate}
See Figure~\ref{fig: small configs} for an illustration of the two configurations.
\end{lem}

@@

@@

% \arrowangle is defined globally in the preamble for easy tweaking

@@

  \draw[propassignment,red] (1.5*\angle + -1*\move:\radius) to[bend left = \arrowangle] (\angle*1:\radius); %p
  \draw[propassignment,red] (1.5*\angle:\radius) to[bend right = \arrowangle] (\angle*2:\radius); %q
  \draw[propassignment,red] (4.5*\angle:\radius) to[bend left = \arrowangle] (\angle*4:\radius); %r

@@

  \draw[propassignment,red] (1.5*\angle + -1*\move:\radius) to[bend right = \arrowangle] (\angle*2:\radius); %p
  \draw[propassignment,red] (5.5*\angle:\radius) to[bend left = \arrowangle] (\angle*5:\radius); %q
  \draw[propassignment,red] (4.5*\angle:\radius) to[bend left = \arrowangle] (\angle*4:\radius); %r

@@

  \draw[propassignment,red] (6.5*\angle:\radius) to[bend left = \arrowangle] (\angle*6:\radius); %p
  \draw[propassignment,red] (5.5*\angle:\radius) to[bend left = \arrowangle] (\angle*5:\radius); %q
  \draw[propassignment,red] (4.5*\angle:\radius) to[bend left = \arrowangle] (\angle*4:\radius); %r

@@

  \draw[propassignment,red] (6.5*\angle:\radius) to[bend right = \arrowangle] (\angle*7:\radius); %p
  \draw[propassignment,red] (5.5*\angle:\radius) to[bend right = \arrowangle] (\angle*6:\radius); %q
  \draw[propassignment,red] (4.5*\angle:\radius) to[bend right = \arrowangle] (\angle*5:\radius); %r

@@

  \draw[propassignment,red] (6.5*\angle:\radius) to[bend right = \arrowangle] (\angle*7:\radius); %p
  \draw[propassignment,red] (5.5*\angle:\radius) to[bend right = \arrowangle] (\angle*6:\radius); %q
  \draw[propassignment,red] (1.5*\angle + 1*\move:\radius) to[bend left = \arrowangle] (\angle*1:\radius); %r

@@

  \draw[propassignment,red] (6.5*\angle:\radius) to[bend right = \arrowangle] (\angle*7:\radius); %p
  \draw[propassignment,red] (1.5*\angle:\radius) to[bend left = \arrowangle] (\angle*1:\radius); %q
  \draw[propassignment,red] (1.5*\angle + \move:\radius) to[bend right = \arrowangle] (\angle*2:\radius); %r

@@

\begin{figure}
\[
\begin{tikzpicture}[baseline=(current bounding box.east),rotate=-20]
\begin{scope}
	\drawWLDfragment[8]{3}{0.4} 
	%\drawnumberspartial % use this to debug
	\newnode[left]{1}{i-1}
	\newnode[below]{2}{i}
	\newnode[below]{7}{m}
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
		\newpropbend{1.7}{7.2}{60}
		\draw[smallpropagator,blue] (\zero+7.8*\step:\radius*1.1) to[bend left = 55] (\zero + 10*\step:\radius*1.1);
		\node at (\zero + 1.2*\step:\radius*0.5) {\footnotesize $p$};
	\end{scope}
	\node[align = center,black] at (\zero + \step*4.5:\radius*0.65) {\em \footnotesize propagators \\ \footnotesize \em inside $p$};
	\draw[propassignment,gray] (\zero + 1.6*\step:\radius) to[bend left = \arrowangle] (\zero + 1*\step:\radius); %p
	\draw[propassignment,gray] (\zero + 7.9*\step:\radius) to[bend left = \arrowangle] (\zero + 7*\step:\radius); 
	\node[align = center,black] at (\zero + 6.8*\step:1.5*\radius) {\em \footnotesize If $m \in I_i$ then \\ \em \footnotesize it was contributed by \\ \em \footnotesize the blue propagator};
\end{scope}
\end{tikzpicture}
\qquad 
\begin{tikzpicture}[baseline=(current bounding box.east),rotate=-20]
	\begin{scope}
	\drawWLDfragment[8]{3}{0.4}  
	%\drawnumberspartial % use this to debug
	\newnode[left]{1}{i}
	\newnode[below]{2}{i+1}
	\newnode[below]{7}{j}
	\centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 1.5*\step:\zero+1.56*\step:\radius);
	\draw[propassignment,gray] (\zero + 1.45*\step:\radius) to[bend left = \arrowangle] (\zero + 1*\step:\radius); %p
	\draw[propassignment,gray] (\zero + 1.61*\step:\radius) to[bend right = \arrowangle] (\zero + 2*\step:\radius); %q 
	\draw[propassignment,gray] (\zero + 7.7*\step:\radius) to[bend left = \arrowangle] (\zero + 7*\step:\radius); %blue
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
		\newpropbend{1.6}{7.2}{40} % q
		\draw[smallpropagator] (\zero+1.5*\step:\radius*1.1) to[bend right = 40] (\zero  - 3*\step:\radius*1.1); % p
		\draw[smallpropagator,blue] (\zero+7.6*\step:\radius*1.1) to[bend left = 55] (\zero + 10*\step:\radius*1.1);
		\node at (\zero + 5*\step:\radius*0.3) {\footnotesize $q$};
		\node at (\zero + 1*\step:\radius*0.6) {\footnotesize $p$};
	\end{scope}
	\node[align = center,black] at (\zero + \step*4.5:\radius*0.75) {\em \footnotesize propagators \\ \footnotesize \em inside $q$};
	\node[align = center] at (\zero + 1.5*\step:\radius*1.5) {\footnotesize \em No \\ \footnotesize \em propagators \\ \footnotesize \em between \\ \footnotesize \em $p$ and $q$ \\ \footnotesize \em here};
	\node[align = center,black] at (\zero + 6.8*\step:1.5*\radius) {\em \footnotesize If $j \in I_i$ then \\ \em \footnotesize it was contributed by \\ \em \footnotesize the blue propagator};
\end{scope}
\end{tikzpicture}
\]
  \caption{The two cases in the proof that no factors of $\Delta_{I_i}$ have degree 3 or more.{\color{violet}First picture: I thought $I_i(p) = i$. Doesn't the arrow say that $I_i(p) = i-1$?}}\label{fig no big factors}
\end{figure}
